fGFPCA dynamic prediction

### 2022-11-09 f-GFPCA.Rmd
fix typos

## Top simulation with a very simple function

@@

- Bloew is the predicted latent functions from local GLMM models

@@

>>>>

## Toy simulation with a very simple function

@@

- Below is the predicted latent functions from local GLMM models

@@

# Next steps:

- Use fastGFPCA to generate more complicated functions
- What happened to the latent gaussian function? Are they just noisy versions of true latent functions? Or it there something wrong with GLMMs? 
- Establish prediction intervals of latent gaussian function
- Write a function to calculate random effects (instead of using predict.fpca.sparse)
